\Title

### 2020-02-17 manuscript/manuscript.tex
Fix some writing

How to choose how many sources will be used and where to locate them are not
trivial decisions and play an important role on the accuracy of the predictions
and the computational resources needed to fit the sources' coefficients.

The chosen distribution of sources should be reproduce the
measured data on the survey points and simultaneously be able to make accurate
predictions of the measured harmonic field on non observed locations.

>>>>

How to choose how many sources to use and where to locate them are not
trivial decisions which play an important role on the accuracy of the
predictions and the computational resources needed to fit the sources'
coefficients.

The chosen distribution of sources should reproduce the measured data on the
survey points and simultaneously be able to make accurate
predictions of the measured harmonic field on non observed locations.
